---
title: "STAT 515 Project Group 8(Word)"
author: "Kushal,Sushanth,Jyoti,Vasudev"
date: "10/03/2021"
output: word_document
---


## Including Plots
Installed packages for the project
Please set the directory to the file downloaded 
```{r}
setwd("D:/STAT 515 Project")
install.packages("gapminder")
install.packages("highcharter")
install.packages("tidyr")
install.packages("tidyverse")
install.packages("ggplot2")
install.packages("devtools")
require(devtools)
install_github('ramnathv/rCharts',force = TRUE)
```
```{r}
library(ggplot2)
```


## Importing Data Sets to Data Frames
Please Load The DataSet from your working Directory
```{r}
source("hw.R")
world <- read.csv("World.csv", sep=",")
World_ <- read.csv("Deaths_B.csv",sep=",")
SDI <- read.csv(file = "Book2.csv")
Deaths <- read.csv("risk_factor_final.csv")
```

## Data Sorrting
Run this sorting process before runing the plots
```{r}
b<- sum(world$Deaths_by_unsafe_sex)
b<-append(b,sum(world$Deaths_by_low_physical_activity))
b<-append(b,sum(world$Deaths_by_smoking))
b<-append(b,sum(world$Deaths_by_alcohol_consumption))
b<-append(b,sum(world$Deaths_by_drug_use))
b<-append(b,sum(world$Deaths_by_diabetes))
b<-append(b,sum(world$Deaths._by_high._blood_pressure))
b<-append(b,sum(world$Deaths_by_unsafe_water))
b<-append(b,sum(world$Deaths_by_unsafe_sanitation))
b<-append(b,sum(world$Deaths_by_air_pollution))


x<-c("unsafe_sex","Low_physical_activity","Smoking","Alcohol","Drug_use","Diabetes","High_BP","Unsafe_water","Unsafe_sanitation","Air_pollution")

riskfact <- data.frame(x,b)
```
## Data Cleaning 
Run this cleaning process before runing the plots
```{r}
world$Deaths_by_unsafe_sex=round(world$Deaths_by_unsafe_sex,digits=0)
world$Deaths_by_low_physical_activity=round(world$Deaths_by_low_physical_activity,digits =0)
world$Deaths_by_smoking=round(world$Deaths_by_smoking,digits = 0)
world$Deaths_by_alcohol_consumption=round(world$Deaths_by_alcohol_consumption,digits = 0)
world$Deaths_by_drug_use=round(world$Deaths_by_drug_use,digits = 0)
world$Deaths_by_diabetes=round(world$Deaths_by_diabetes,digits=0)
world$Deaths._by_high._blood_pressure=round(world$Deaths._by_high._blood_pressure,digits = 0)
world$Deaths_by_unsafe_water=round(world$Deaths_by_unsafe_water,digits = 0)
world$Deaths_by_unsafe_sanitation=round(world$Deaths_by_unsafe_sanitation,digits = 0)
world$Deaths_by_air_pollution=round(world$Deaths_by_air_pollution,digits = 0)
```
## Figure1: Total number of deaths by risk factors
```{r}
ggplot(data=riskfact, aes(x=reorder(x,b), y=b,scientific= FALSE))+ 
  geom_bar(stat="identity", color="black",fill="#69b3a2")+
  scale_y_continuous(breaks=c(20000000,40000000,60000000,80000000,100000000,120000000,140000000,160000000),
                     labels=c('20000000' = '20m','40000000' = '40m','60000000'='60m','80000000'='80m','100000000'='100m','120000000'='120m','140000000'='140m','160000000'='160m'))+
   coord_flip()+labs(x="RISK FACTORS",y="NUMBER OF DEATHS",title="DEATHS DUE TO ALL THE RISK FACTORS")+hw
```

## Figure2: Yearly death caused by different risk factors

```{r}
#scatter plot
library(highcharter)
data(gapminder, package = "gapminder")
library(tidyr)
library(tidyverse)

# generate graph
h <- highchart() %>% 
  hc_xAxis(categories = world$Year) %>% 
  hc_add_series(name = "Smoking", 
                data = world$Deaths_by_smoking) %>% 
  hc_add_series(name = "Unsafe sex", 
                data = world$Deaths_by_unsafe_sex) %>%
  hc_add_series(name = "Low Physical activity", 
                data = world$Deaths_by_low_physical_activity) %>%
  hc_add_series(name = "Alcohol", 
                data = world$Deaths_by_alcohol_consumption) %>%
  hc_add_series(name = "Drug Use", 
                data = world$Deaths_by_drug_use)%>%
  hc_add_series(name = "Diabeties", 
                data = world$Deaths_by_diabetes)%>%
  hc_add_series(name = "High Blood Pressure", 
                data = world$Deaths._by_high._blood_pressure)%>%
  hc_add_series(name = "Unsafe Water", 
                data = world$Deaths_by_unsafe_water)%>%
  hc_add_series(name = "Unsafe Sanitation", 
                data = world$Deaths_by_unsafe_sanitation)%>%
  hc_add_series(name = "Air polution", 
                data = world$Deaths_by_air_pollution)%>%
  hc_title(text = "Trends Of Various Risk Factors",
           margin = 20, 
           align = "center",
           style = list(color = "steelblue")) %>% 
  hc_subtitle(text = "2000 To 2017",
              align = "center",
              style = list(color = "#2b908f", 
                           fontWeight = "bold")) %>% 
  hc_legend(align = "right", 
            verticalAlign = "top",
            layout = "vertical", 
            x = 0, 
            y = 100) %>%
  hc_tooltip(crosshairs = TRUE, 
             backgroundColor = "#fabea5",
             shared = TRUE, 
             borderWidth = 4) %>% 
  hc_exporting(enabled = TRUE)%>%
  hc_xAxis(title = list(text = "Years"),
           alternateGridColor = "#cccccc",size=15)%>%
  hc_yAxis(title = list(text ="Deaths"))
h
```

## Figure 3: Trend of deaths in countries with different SDI

```{r}
library(rCharts)
library(reshape)
data(SDI,package = 'ggplot2')
SDI$Deaths =  round(SDI$Deaths)
SDI$Deaths=  as.numeric(SDI$Deaths)
n3 <- nPlot(Deaths ~ Country,group = 'Risk_factor',data = SDI,type = 'multiBarHorizontalChart',height=500,width=800)
n3$addParams(width = 600, height = 300, dom = 'chart1',title = "Percentage of Employed who are Senior Managers")
n3
```

## Figure 4: Perspective of the Risk Factors. (Deaths in millions)

```{r}
library(dplyr)
library(tidyverse)
library(highcharter) 



World_$Deaths_A =  round(World_$Deaths_A)
World_$Deaths_A =  as.numeric(World_$Deaths_A)

v1 <- data_to_boxplot(world , var=Deaths_by_smoking   ,name = "Smoking")
v2 <- data_to_boxplot(world , var=Deaths_by_unsafe_sex   ,name = "Unsafe Sex")
v3 <- data_to_boxplot(world , var=Deaths_by_low_physical_activity   ,name = "Low Physical Activity")
v4 <- data_to_boxplot(world , var=Deaths_by_drug_use   ,name = "Drug Use")
v5 <- data_to_boxplot(world , var=Deaths_by_diabetes   ,name = "Diabetes")
v6 <- data_to_boxplot(world , var=Deaths._by_high._blood_pressure   ,name = "High Blood Pressure")
v7 <- data_to_boxplot(world , var=Deaths_by_unsafe_water   ,name = "Unsafe Water")
v8 <- data_to_boxplot(world , var=Deaths_by_alcohol_consumption   ,name = "Alcohol Consumption")
v9 <- data_to_boxplot(world , var=Deaths_by_unsafe_sanitation   ,name = "Unsafe Sanitation")
v10 <- data_to_boxplot(world , var=Deaths_by_air_pollution   ,name = "Air Pollution")

highchart() %>%  hc_xAxis(title = list(text = "Risk Factors",fontWeight="bold",categories = world$Country)) %>%
  hc_yAxis(title=list(text="Deaths",fontWeight="bold"))%>%
  hc_add_series_list(v1)%>%
  hc_add_series_list(v2)%>%
  hc_add_series_list(v3)%>%
  hc_add_series_list(v4)%>%
  hc_add_series_list(v5)%>%
  hc_add_series_list(v6)%>%
  hc_add_series_list(v7)%>%
  hc_add_series_list(v8)%>%
  hc_add_series_list(v9)%>%
  hc_add_series_list(v10)%>%
    hc_title(text = "Perspective Of The Risk Factors(In Millions)",
           margin = 20, 
           align = "center",
           style = list(color = "steelblue")) %>% 
  hc_subtitle(text = "Box Plot For Risk Factor",
              align = "center",
              style = list(color = "#2b908f", 
                           fontWeight = "bold")) %>% 
  hc_legend(align = "right", 
            verticalAlign = "top",
            layout = "vertical", 
            x = 0, 
            y = 100) %>%
  hc_exporting(enabled = TRUE)%>%
  hc_xAxis(title = list(text = "Risk Factors"),size=15)%>%
  hc_yAxis(title = list(text ="Deaths"))
```






